Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-11 paper-plan/paper-plan.tex
Progressive heuristics thing

\subsection{}

>>>>

\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}

In this paper a probabilistic plan graph heuristic is described which computes
information about the interaction between actions and between propositions.
This information is used to find better relaxed plans to compute the
probability of success. This information guides a forward state space search
for high probability, non-branching seed plans. These plans are then used in
a planning and scheduling system that handles unexpected outcomes by runtime
replanning.

\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
